The evolution of the transcriptome of mammalian placentas

### 2016-09-12 manuscript/manuscript.Rnw
load placental_classification

>>>>

<<placental_classification,echo=FALSE,results="hide",cache.extra=file.info(dir("../data","placenta.*classification.*",full.names=TRUE))[,"mtime"]>>=
placenta_classification <- fread("../data/placental_classification.txt")
load("../data/placenta_classification_p")
for (mf.bp in c("mf","bp")) {
    for (class in c("interdigitation","barrier","shape")) {
        load(paste0("../data/placenta_classification_go_",mf.bp,"_",class))
    }
}
